Revisiting the hydrodynamic modulation of short waves by longer waves

### 2024-09-24 paper/paper.tex
Discussion

>>>>

The solutions presented here, analytical and numerical alike, are valid only
for certain scales of short and long waves.
Specifically, the wave action conservation equation, introduced by
\citet{bretherton1968wavetrains}, requires that the ambient velocity is slowly
varying on the time scales of short waves, \textit{i.e.}
$|\partial U / \partial x| \ll k |U|$
and $|\partial U / \partial t| \ll \sigma |U|$.
This implies $k_L \ll k$ and $|\sigma_L| \ll \sigma|$, respectively.
Another requirement is for the short-waves to remain linear, which implies
$a k \ll 1$.
Furthermore, the short waves examined here do not include the effects of
surface tension (gravity-capillary waves) or intermediate or shallow water.
Within these limits, the crest-action conservation equations provide an
elegant and relatively simple framework to study the hydrodynamic modulation
of short waves by longer waves.
This approach, of course, isolates this particular process from others
dominant modulation and nonlinear transfer processes, such as wave growth
by wind, wave dissipation, and aerodynamic sheltering by the longer waves.

Although in this paper we only explored the wavenumbers 1 and 10 for the long
and short waves, respectively ($k/k_L = 10$), the results are not sensitive
to different values of $k_L$, provided that the amplitude $a_L$ is set such that
the long-wave steepness $\varepsilon_L = a_L / k_L$ is the same.
Numerical simulations with that compare $k/k_L = 10$ and $k/k_L = 100$ show
very little sensitivity $k/k_L$ (not shown), consistent with the results of
\citet{longuet1987propagation}.
Specifically, the short-wave steepness modulation is 1\% larger at
$\varepsilon_L = 0.27$ for $k/k_L = 10$ compared to $k/k_L = 100$, and 4\%
larger at $\varepsilon_L = 0.4$.
This suggests that as long as $k/k_L \gg 1$, the modulation amplitude is
largely independent of the ratio $k/k_L$.

Despite several studies that provided qualitatively similar steady solutions
for the short-wave modulation by long waves
\citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,henyey1988energy,zhang1990evolution},
it was not obvious from the governing equations that the fully-nonlinear
steady solutions should exist.
\citet{peureux2021unsteady} examined this problem numerically and found that
the solutions are stable only if the short-wave field is initialized from
a prior steady solution of the form of that from \citet{longuet1960changes}.
If the short-wave field is instead initialized from a uniform field, they
found that the short-wave amplitude, and thus steepness as well, grow
unsteadily.
However, in this study we demonstrate that the unsteady steepening of short
waves only occurs in the case of a sudden appearance of long waves, where
the velocity fields induced by the long waves act in their full capacity
on the short waves that have not yet had time to "lock in" to the long-wave
crests.
In such a hypothetical scenario, sudden forcing on short waves causes the
modulation pattern to detach itself from the long-wave crests and to propagate
at the short-wave group speed.
When this occurs, the modulated short-waves are no longer in a stabilizing
resonance with the surface convergence and divergence induced by the long-wave
orbital velocity, and each long-wave passage further destabilizes the short-wave
field, causing it to steepen indefinitely.

Another important consideration of the hydrodynamic modulation process is
whether it should somehow be accounted for in phase-averaged spectral wave
models used for regional and global wave forecasting. 
In the early days of spectral wave modeling, \citet{willebrand1975energy}
examined the effect of a wave spectrum on the short-wave group velocity,
and found the effect of up to several percent modulation.
For a practical implementation in a spectral wave model, this would have to
incur an additional loop over all frequencies for each short-wave frequency.
It was thus not deemed practical to include this effect in wave models at the time.
However, with the recent advances in machine learning and phase-resolving modeling
of short waves, the effect of wave-modulation deserves re-examination.

TODO Implications for spectral wave models and wind input to short waves.
